SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-02-09 sedona-ieice16/revision/resources/paper_4p.tex
SEDONA updates fitting 4 pages

\noindent
The rest of this letter is organized as follows. 
{\color{blue}We next elaborate on the proposed timing protocol. 
In turn, we evaluate the performance of the scheme using real workloads. 
\shorten{Finally, we conclude this letter.}
}

@@

{\bf A Running Example.} 
%As motivated by our prior work~\cite{Currim}, 
%we configure a timing environment by i) stopping non-critical daemons, 
%ii) activating the Network Timing Protocol daemon, and 
%iii) switching off particular CPU features\cite{intel15,intelSpeed15} if any (Step 1). 
{\color{blue}
First, we set up the same measurement environment as described earlier in Section~\ref{sec:intro}, 
to eliminate known timing factors in advance (Step~1).}

@@

\begin{figure}[ht]
	\centering
	\subfigure[PUT128 with 800 Samples]{
		%\includegraphics[width=0.223\textwidth]{put128_empv4.eps}
		\includegraphics[width=0.224\textwidth]{put128_empv4_new.eps}
		\label{fig:reg_put128}
	}
	\subfigure[Dual-PUT256 Samples]{
		%\includegraphics[width=0.223\textwidth]{dual_et_put256_empv4.eps}
		\includegraphics[width=0.224\textwidth]{dual_et_put256_empv4.eps}
		\label{fig:raw_put128}
	}
	%\vspace{-0.1in}    
	\subfigure[Zooming in on the $L$-shape]{
		\includegraphics[width=0.224\textwidth]{zooming_in_dual_et_put256_empv4.eps}
		\label{fig:dual_put256_liters}
	}
	\subfigure[The Central Cluster]{
		\includegraphics[width=0.224\textwidth]{dual_et_clump_put256_empv4.eps}
		\label{fig:dual_et_put256_cluster}
        }
    \caption{Successive Scatter Plots of PUT128 with 800 samples 
    (equivalent to Dual-PUT256 with 400 samples) in Steps~2---4~\label{fig:put128_plot}} 
    \vspace{-0.2in}     
\end{figure}

@@

We then perform Step~5, which computes 
the maximum process time and standard deviation 
of PT (process time, note the switch in emphasis from elapsed time 
to process time) of the daemon processes 
(e.g. {\tt cifsd}, {\tt flush-9:0}, {\tt jbd2/md0-8}, 
{\tt kblockd/0}, {\tt khugepaged}, {\tt md0\_raid1}, and {\tt ntpd})
observed in the central cluster samples in Fig.~\ref{fig:dual_et_put256_cluster}. 
\shorten{In the running example the maximum PT of those daemons was under 4 msec, 
and their standard deviation was just about 1 msec.}

In Step~6 we identify, for each daemon in the \hbox{$L$-samples}, 
those that are actual long-running daemon
executions.  We define such executions as those whose PT 
is over two standard deviations above the maximum PT for
that daemon in the central cluster samples. 
In the running example  {\tt flush-9:0}, 
{\tt jbd2/md0-8}, and {\tt md0\_raid1} 
are determined as infrequent, long-running.
We also identify ``extra'' infrequent daemons: those
found only in the $L$-samples but not in the central cluster. 
The running example reveals the following extra daemons: 
{\tt bash}, {\tt grep}, {\tt rhn\_check}, {\tt rhnsd}, {\tt rhsmcertd}, 
{\tt rhsmcertd-worke}, and {\tt sshd}.

{\color{blue}
For each of the infrequent daemons 
we use a heuristic to determine the daemon's periodicity:}
the daemon must occur regularly in a sequence of samples.
For instance, the {\tt rhn\_check} daemon appears 
roughly every 112 samples (which corresponds to very close to every four 
hours). Four others ({\tt flush-9:0}, {\tt jbd2/md0-8}, 
{\tt md0\_raid1}, and {\tt rhn\_check}) all occur together 
(in those two outliers in Fig.~\ref{fig:raw_put128}) and 
  have a periodicity of about every 559 samples
  (5x longer, or just about 20 hours). 
%  It is important only which samples a given daemon shows up 
%  in; we don't care in this heuristic whether daemons are co-occurring.

@@

In Step 8 we repeat Steps 1--6, but instead with the much-longer running
PUT16384 (4.5 hours per \hbox{sample} versus 2 minutes), to see 
if any of our identified \hbox{infrequent} daemons are actually frequent 
at that much longer PUT execution time. 
We find some frequent daemon processes appearing in both of the 
clusters of dual-PUT256 and dual-PUT32768{\color{blue}, each consisting of 
pairs of two successive samples of PUT128 and PUT16384}: 
{\tt flush-9.0}, {\tt jbd2/md0-8}, {\tt kblock/0}, {\tt md0\_raid1}, 
and {\tt ntpd}. That said, the central cluster also contains other
  processes not seen in the \hbox{dual-PUT256} central cluster: 
  {\tt grep}, {\tt rhn\_check}, {\tt rhnsd}, {\tt rhsmcertd}, 
  {\tt rhsmcertd-worke}, and {\tt sshd}. 
  But these daemons were categorized in the \hbox{dual-PUT256} analysis as {\em
  infrequent}, several having \hbox{periodicities} estimated at four or twenty hours.
When {\color{blue}PUT128} had a ``short'' 
program time {\color{blue}(or, two minutes)}, daemons with a periodicity of
hours are \hbox{infrequent}. But with {\color{blue}PUT16384} 
with a ``long'' program time {\color{blue}(or, 4.5 hours)}, some of those daemons are now frequent, and appear in the central cluster.

@@

\begin{table}[ht]
\centering
{\scriptsize
\begin{tabular}{|p{1.2cm}|c|c|p{1cm}|p{1.45cm}|} \hline
{\tiny Process}  & {\tiny Cutoff PT} & {\tiny Cutoff PT} & {\tiny Task}  & {\tiny{\bf Final }} \\
{\tiny Name} & {\tiny on PUT128}  & {\tiny on PUT16K} & {\tiny Time} & {\tiny {\bf Cutoff PT}} \\\hline
%{\tiny Process}  & {\tiny Cutoff PT} & {\tiny Cutoff PT} & {\tiny Task}  & {\tiny{\bf Final }} \\
% Name & on PUT128  & on PUT16K & Time & {\bf Cutoff PT} \\\hline
{\tt bash} & 1 msec & --- & --- & {\bf 1 msec} \\ \hline
{\tt flush-9:0} & 64 msec & --- & $< 1$ hour & {\bf 64 msec} \\
                & ---     & 48 msec & $\geq 1$ hour & {\bf 48 msec} \\ \hline
{\tt grep }     & 1 msec & 12 msec & --- & {\bf 12 msec}\\ \hline
{\tt jbd2/md0-8} & 4 msec & --- & $< 1$ hour & {\bf 4 msec} \\
                & ---     & 11 msec & $\geq 1$ hour & {\bf 11 msec} \\ \hline
{\tt md0\_raid1} & 35 msec & ---     & $< 1$ hour  & {\bf 35 msec}\\
                 & ---     & 51 msec & $\geq 1$ hour & {\bf 51 msec} \\ \hline
{\tt rhn\_check}  & 281 msec & --- & $< 12$ min & {\bf 281 msec} \\
                 &  --- & 12,828 msec & $\geq 12$ min & {\bf 12,828 msec}\\ \hline
{\tt rhnsd} & 2 msec & --- & $< 12$ min & {\bf 2 msec} \\
            & ---    & 12 msec &$\geq 12$ min & {\bf 12 msec} \\ \hline
{\tt rhsmcertd}  & 1 msec & 1 msec & --- & {\bf 1 msec} \\  \hline
{\tt rhsmcertd}  & 57 msec & --- & $< 12$ min & {\bf 57 msec} \\
{\tt -worke}           &  --- & 119 msec  & $\geq 12$ min & {\bf 119 msec}\\ \hline
{\tt sshd} & 2 msec & 23 msec & --- & {\bf 23 msec}\\ \hline
\end{tabular}
}
\caption{Collected Infrequent, Long-running Daemons and Their Final Cutoff
  Process Time \hbox{(Step~9)}\label{tab:final_infrequent_cutoff}}
  \vspace{-0.4in}
\end{table}

@@

\section{Evaluation}
\label{sec:eval}
\vspace{-0.07in}
We now evaluate the \hbox{performance} of SEDONA 
compared to that of the conventional timing scheme, termed ORG, based on 
elapsed time.
Our experiments were conducted on a \hbox{machine}
described in Table~\ref{tab:machine_config}. 
\begin{table}[h]
\vspace{-0.2in}
\begin{center}
{\scriptsize
\begin{tabular}{|l|p{7cm}|}\hline
OS & Red Hat Ent. Linux (RHEL) 6.4 with a kernel of 2.6.32 \\ \hline
CPU & Intel Core i7-870 Lynnfield 2.93GHz quad-core \hbox{processor}\shorten{ on a LGA 1156 95W motherboard}\\ \hline
RAM & 4GB of DDR3 1333 dual-channel memory\\ \hline
HDD & Western Digital Caviar Black 1TB 7200rpm SATA Drive\\ \hline
\end{tabular}
}
\end{center}
\caption{Machine Configurations\label{tab:machine_config}}
\vspace{-0.3in}
\end{table}

@@

@@

\begin{figure}[t]
	\centering
	\subfigure[{\color{blue}SORT - Standard Deviation}]{
		\includegraphics[scale=0.31]{sort_std.eps}
		\label{fig:sort_std}
	}
	\subfigure[{\color{blue}SORT - Relative Error}]{
		\includegraphics[scale=0.31]{sort_re.eps}
		\label{fig:sort_re}
	}
	\subfigure[{\color{blue}MM - Standard Deviation}]{
		\includegraphics[scale=0.31]{matc_std.eps}
		\label{fig:matc_std}
	}
	\subfigure[{\color{blue}MM - Relative Error}]{
		\includegraphics[scale=0.31]{matc_re.eps}
		\label{fig:matc_re}
	}
	\vspace{-.1in}
	\caption{{\color{blue}Performance Comparison on Real-world Programs~\label{fig:synprog_test}}}
\vspace{-.2in}
\end{figure}

@@

\vspace{-0.1in}
\begin{table}[t]
\centering
{
\scriptsize
\begin{tabular}{|p{0.18cm}|R{1.14cm}|R{1.14cm}|R{0.64cm}|R{1cm}|R{0.97cm}|R{0.97cm}|} \hline
 		  & \multicolumn{2}{c|}{{\tiny Execution Time (ms)}} & \multicolumn{2}{c|}{{\tiny Standard}}   & \multicolumn{2}{c|}{\multirow{2}{*}{{\tiny Relative Error}}}\\ \cline{2-3}
 & \multicolumn{1}{c|}{{\tiny{ORG}}}  & \multicolumn{1}{c|}{{\tiny{SEDONA}}} & \multicolumn{2}{c|}{{\tiny Deviation (ms)}}  & \multicolumn{2}{c|}{}\\ \cline{4-7}	
 & \multicolumn{1}{c|}{{\tiny{(in ET)}}} & \multicolumn{1}{c|}{{\tiny{(in PT)}}} & {\tiny{ORG}} & {\tiny{SEDONA}} & \multicolumn{1}{c|}{{\tiny{ORG}}}& \multicolumn{1}{c|}{{\tiny{SEDONA}}}\\ \hline
{{\tt 400}} & 454 & 445 & {3} & {2} & {6$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 401}} & 536,639 & 528,517 & {1,185} & {1,161} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 403}} & 26,109	& 25,695 & {138} & {96} & {5$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 410}} & 7,938 & 7,801 & {46} & {19} & {6$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 416}} & 1,015,342 & 999,846 & {965} & {876} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\%% V
{{\tt 429}} & 235,811 & 232,209 & {623} & {600} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 433}} & 480,586 & 473,256  & {743} & {725} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ %% V
{{\tt 434}} & 16,495  & 16,242  & {\color{blue}{75}} & {\color{blue}{7}} & {\color{blue}{5$\times$10$^{-3}$}} & {\color{blue}{5$\times$10$^{-4}$}}\\
{{\tt 435}} & 990,575 & 975,445  & {947} & {900} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
{{\tt 436}} & 1,160,742 & 1,143,078   & {3,914} & {3,843} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 437}} & 581,635 & 572,775 & {1,492} & {1,475}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 444}} & 591,201 & 582,229 & {294} & {281}  & {5$\times$10$^{-4}$} & {5$\times$10$^{-4}$}\\
{{\tt 445}} & 84,435  & 83,164  & {91} & {28}  & {1$\times$10$^{-3}$} & {3$\times$10$^{-4}$}\\
{{\tt 447}} & 521,846 & 513,493  & {150} & {108}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 450}} & 341,030 & 335,848  & {99} & {91}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 453}} & 258,797 & 254,496  & {623} & {582}  & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 454}} & 1,721,804 & 1,695,613  & {678} & {627}  & {4$\times$10$^{-4}$} & {4$\times$10$^{-4}$}\\
{{\tt 456}} & 410,533 & 404,328  & {85} & {50}  & {2$\times$10$^{-4}$} & {1$\times$10$^{-4}$}\\
{{\tt 458}} & 589,541 & 580,591  & {542} & {513} &  {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 459}} & 798,917 & 786,726  & {2,143} & {2,132}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 462}} & 595,188 & 586,120  & {3,326} & {3,274}  & {6$\times$10$^{-3}$} & {6$\times$10$^{-3}$}\\
{{\tt 464}} & 649,838 & 639,939  & {601} & {563}  & {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 465}} & 895,754 & 882,106  & {883} & {797}  & {1$\times$10$^{-3}$} & {1$\times$10$^{-3}$}\\
{{\tt 470}}	& 349,830 & 344,510 & {143} & {94} & {4$\times$10$^{-4}$} & {3$\times$10$^{-4}$}\\
{{\tt 471}} & 367,589 & 361,959  & {2,114} & {2,072} & {6$\times$10$^{-4}$} & {6$\times$10$^{-4}$}\\
{{\tt 473}} & 362,587 & 357,090  & {359} & {317} &  {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
%{{\tt 481}} & \multicolumn{4}{c}{Runtime Error}\\
{{\tt 482}} & 654,208	 & 644,223  & {2,436} & {2,392} &   {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\ %% V
%{{\tt 483}} & \multicolumn{4}{c}{Out-of-Scope}\\
{{\tt 998}} & 128	 & 127  & {0.6} & {0.6} &  {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 999}} & 128 &  127 & {0.8} & {0.6} &  {6$\times$10$^{-3}$} & {5$\times$10$^{-3}$}\\ \hline 
\multicolumn{3}{|r|}{Averages} & 852 & 815 &  {3$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ \hline
\end{tabular}
}
\caption{Performance Evaluation on the SPEC Benchmarks\label{tab:spec_real}}
\vspace{-0.25in}
\end{table}

>>>>

\noindent
{\color{blue}The rest is organized as follows. 
We next elaborate on the proposed timing protocol. In turn we evaluate the performance of the scheme using real workloads. 
\shorten{Finally, we conclude this letter.}
}

@@

{\bf A Running Example.} 
%As motivated by our prior work~\cite{Currim}, 
%we configure a timing environment by i) stopping non-critical daemons, 
%ii) activating the Network Timing Protocol daemon, and 
%iii) switching off particular CPU features\cite{intel15,intelSpeed15} if any (Step 1). 
{\color{blue}
First, we set up the same measurement environment as described earlier in Section~\ref{sec:intro}, 
to eliminate known timing factors (Step~1).}

@@

\begin{figure}[ht]
	\centering
	\subfigure[PUT128 with 800 Samples]{
		%\includegraphics[width=0.223\textwidth]{put128_empv4.eps}
		\includegraphics[width=0.224\textwidth]{put128_empv4_new.eps}
		\label{fig:reg_put128}
	}
	\subfigure[Dual-PUT256 Samples]{
		%\includegraphics[width=0.223\textwidth]{dual_et_put256_empv4.eps}
		\includegraphics[width=0.224\textwidth]{dual_et_put256_empv4.eps}
		\label{fig:raw_put128}
	}
	%\vspace{-0.1in}    
	\subfigure[Zooming in on the $L$-shape]{
		\includegraphics[width=0.224\textwidth]{zooming_in_dual_et_put256_empv4.eps}
		\label{fig:dual_put256_liters}
	}
	\subfigure[The Central Cluster]{
		\includegraphics[width=0.224\textwidth]{dual_et_clump_put256_empv4.eps}
		\label{fig:dual_et_put256_cluster}
        }
    \caption{Successive Scatter Plots of PUT128 with 800 samples 
    (equivalent to Dual-PUT256 with 400 samples) in Steps~2---4~\label{fig:put128_plot}} 
    \vspace{-0.3in}     
\end{figure}

@@

We then perform Step~5, which computes 
the maximum process time and standard deviation 
of PT \shorten{(process time, note the switch in emphasis from elapsed time 
to process time)} of the daemon processes
%(e.g. {\tt cifsd}, {\tt flush-9:0}, {\tt jbd2/md0-8}, 
%{\tt kblockd/0}, {\tt khugepaged}, {\tt md0\_raid1}, and {\tt ntpd})
such as {\tt cifsd}, etc. 
observed in the central cluster samples in Fig.~\ref{fig:dual_et_put256_cluster}. 
\shorten{In the running example the maximum PT of those daemons was under 4 msec, 
and their standard deviation was just about 1 msec.}

In Step~6 we identify, for each daemon in the \hbox{$L$-samples}, 
those that are actual long-running daemon
executions.  We define such executions as those whose PT 
is over two standard deviations above the maximum PT for
that daemon in the central cluster samples. 
In the running example  {\tt flush-9:0}, 
{\tt jbd2/md0-8}, and {\tt md0\_raid1} 
are determined as infrequent, long-running.
%We also identify ``extra'' infrequent daemons: those
%found only in the $L$-samples but not in the central cluster. 
%The running example reveals the following extra daemons: 
%{\tt bash}, {\tt grep}, {\tt rhn\_check}, {\tt rhnsd}, {\tt rhsmcertd}, 
%{\tt rhsmcertd-worke}, and {\tt sshd}.
{\color{blue}We also identify ``extra'' infrequent daemons, 
found only in the $L$-samples but not in the central cluster.}

{\color{blue}
For each of the infrequent daemons 
we use a heuristic to determine the daemon's periodicity:}
the daemon must occur regularly in a sequence of samples.
For instance, the {\tt rhn\_check} daemon appears 
roughly every 112 samples (which corresponds to very close to every four 
hours). 
%Four others ({\tt flush-9:0}, {\tt jbd2/md0-8}, 
%{\tt md0\_raid1}, and {\tt rhn\_check}) all occur together 
%(in those two outliers in Fig.~\ref{fig:raw_put128}) and 
%  have a periodicity of about every 559 samples
%  (5x longer, or just about 20 hours). 
{\color{blue}Four others all occur together and have a periodicity of about every 559 samples 
(5x longer, or just about 20 hours)}. 
%  It is important only which samples a given daemon shows up 
%  in; we don't care in this heuristic whether daemons are co-occurring.

@@

In Step 8 we repeat Steps 1--6, but instead with the much-longer running
PUT16384 (4.5 hours per \hbox{sample} versus 2 minutes), to see 
if any of our identified \hbox{infrequent} daemons are actually frequent 
at that much longer PUT execution time. 
We find some frequent daemon processes appearing in both of the 
clusters of dual-PUT256 and dual-PUT32768{\color{blue}, each consisting of 
pairs of two successive samples of PUT128 and PUT16384}.\shorten{: 
{\tt flush-9.0}, {\tt jbd2/md0-8}, {\tt kblock/0}, {\tt md0\_raid1}, 
and {\tt ntpd}.} 
%That said, the central cluster also contains other
%  processes not seen in the \hbox{dual-PUT256} central cluster: 
%  {\tt grep}, {\tt rhn\_check}, {\tt rhnsd}, {\tt rhsmcertd}, 
%  {\tt rhsmcertd-worke}, and {\tt sshd}. 
That said, the central cluster also contains other
  processes not seen in the \hbox{dual-PUT256} central cluster{\color{blue}, 
  such as {\tt grep}, {\tt rhn\_check}, etc.}
  But these daemons were categorized in the \hbox{dual-PUT256} analysis as {\em
  infrequent}, several having \hbox{periodicities} estimated at four or twenty hours.
When {\color{blue}PUT128} had a ``short'' 
program time {\color{blue}(or, two minutes)}, daemons with a periodicity of
hours are \hbox{infrequent}. But with {\color{blue}PUT16384} 
with a ``long'' program time {\color{blue}(or, 4.5 hours)}, some of those daemons are now frequent, and appear in the central cluster.

@@

\vspace{-0.2in}
\begin{table}[ht]
\centering
{\tiny
\begin{tabular}{|p{1.2cm}|c|c|p{1cm}|p{1.45cm}|} \hline
{\tiny Process}  & {\tiny Cutoff PT} & {\tiny Cutoff PT} & {\tiny Task}  & {\tiny{\bf Final }} \\
{\tiny Name} & {\tiny on PUT128}  & {\tiny on PUT16K} & {\tiny Time} & {\tiny {\bf Cutoff PT}} \\\hline
%{\tiny Process}  & {\tiny Cutoff PT} & {\tiny Cutoff PT} & {\tiny Task}  & {\tiny{\bf Final }} \\
% Name & on PUT128  & on PUT16K & Time & {\bf Cutoff PT} \\\hline
{\tt bash} & 1 msec & --- & --- & {\bf 1 msec} \\ \hline
{\tt flush-9:0} & 64 msec & --- & $< 1$ hour & {\bf 64 msec} \\
                & ---     & 48 msec & $\geq 1$ hour & {\bf 48 msec} \\ \hline
{\tt grep }     & 1 msec & 12 msec & --- & {\bf 12 msec}\\ \hline
{\tt jbd2/md0-8} & 4 msec & --- & $< 1$ hour & {\bf 4 msec} \\
                & ---     & 11 msec & $\geq 1$ hour & {\bf 11 msec} \\ \hline
{\tt md0\_raid1} & 35 msec & ---     & $< 1$ hour  & {\bf 35 msec}\\
                 & ---     & 51 msec & $\geq 1$ hour & {\bf 51 msec} \\ \hline
{\tt rhn\_check}  & 281 msec & --- & $< 12$ min & {\bf 281 msec} \\
                 &  --- & 12,828 msec & $\geq 12$ min & {\bf 12,828 msec}\\ \hline
{\tt rhnsd} & 2 msec & --- & $< 12$ min & {\bf 2 msec} \\
            & ---    & 12 msec &$\geq 12$ min & {\bf 12 msec} \\ \hline
{\tt rhsmcertd}  & 1 msec & 1 msec & --- & {\bf 1 msec} \\  \hline
{\tt rhsmcertd}  & 57 msec & --- & $< 12$ min & {\bf 57 msec} \\
{\tt -worke}           &  --- & 119 msec  & $\geq 12$ min & {\bf 119 msec}\\ \hline
{\tt sshd} & 2 msec & 23 msec & --- & {\bf 23 msec}\\ \hline
\end{tabular}
}
\caption{Collected Infrequent, Long-running Daemons and Their Final Cutoff
  Process Time \hbox{(Step~9)}\label{tab:final_infrequent_cutoff}}
  \vspace{-0.3in}
\end{table}

@@

\section{Evaluation}
\label{sec:eval}
\vspace{-0.07in}
We now evaluate the \hbox{performance} of SEDONA 
compared to that of the conventional timing scheme, termed ORG, based on 
elapsed time.
Our experiments were conducted on a \hbox{machine}
described in Table~\ref{tab:machine_config}. 
\begin{table}[h]
\vspace{-0.2in}
\begin{center}
{\tiny
\begin{tabular}{|l|p{7cm}|}\hline
OS & Red Hat Ent. Linux (RHEL) 6.4 with a kernel of 2.6.32 \\ \hline
CPU & Intel Core i7-870 Lynnfield 2.93GHz quad-core \hbox{processor}\shorten{ on a LGA 1156 95W motherboard}\\ \hline
RAM & 4GB of DDR3 1333 dual-channel memory\\ \hline
HDD & Western Digital Caviar Black 1TB 7200rpm SATA Drive\\ \hline
\end{tabular}
}
\end{center}
\caption{Machine Configurations\label{tab:machine_config}}
\vspace{-0.35in}
\end{table}

@@

\vspace{-.2in}
\begin{figure}[h]
	\centering
	\subfigure[{\color{blue}SORT - Standard Deviation}]{
		\includegraphics[scale=0.31]{sort_std.eps}
		\label{fig:sort_std}
	}
%	\subfigure[{\color{blue}SORT - Relative Error}]{
%		\includegraphics[scale=0.31]{sort_re.eps}
%		\label{fig:sort_re}
%	}
	\subfigure[{\color{blue}MM - Standard Deviation}]{
		\includegraphics[scale=0.31]{matc_std.eps}
		\label{fig:matc_std}
	}
%	\subfigure[{\color{blue}MM - Relative Error}]{
%		\includegraphics[scale=0.31]{matc_re.eps}
%		\label{fig:matc_re}
%	}
	\vspace{-.1in}
	\caption{{\color{blue}Performance Comparison on Real-world Programs~\label{fig:synprog_test}}}
\vspace{-.2in}
\end{figure}

@@

@@

\vspace{-0.1in}
\begin{table}[t]
\centering
{
\tiny
\begin{tabular}{|p{0.1cm}|R{1.1cm}|R{1.1cm}|R{0.6cm}|R{0.6cm}|R{0.97cm}|R{0.97cm}|} \hline
 		  & \multicolumn{2}{c|}{{\tiny Execution Time (ms)}} & \multicolumn{2}{c|}{{\tiny Standard}}   & \multicolumn{2}{c|}{\multirow{2}{*}{{\tiny Relative}}}\\ \cline{2-3}
 & \multicolumn{1}{c|}{{\tiny{ORG}}}  & \multicolumn{1}{c|}{{\tiny{SED.}}} & \multicolumn{2}{c|}{{\tiny Deviation (ms)}}  & \multicolumn{2}{c|}{{\tiny Error}}\\ \cline{4-7}	
 & \multicolumn{1}{c|}{{\tiny{(in ET)}}} & \multicolumn{1}{c|}{{\tiny{(in PT)}}} & {\tiny{ORG}} & {\tiny{SED.}} & \multicolumn{1}{c|}{{\tiny{ORG}}}& \multicolumn{1}{c|}{{\tiny{SED.}}}\\ \hline
{{\tt 400}} & 454 & 445 & {3} & {2} & {6$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 401}} & 536,639 & 528,517 & {1,185} & {1,161} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 403}} & 26,109	& 25,695 & {138} & {96} & {5$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 410}} & 7,938 & 7,801 & {46} & {19} & {6$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 416}} & 1,015,342 & 999,846 & {965} & {876} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\%% V
{{\tt 429}} & 235,811 & 232,209 & {623} & {600} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 433}} & 480,586 & 473,256  & {743} & {725} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ %% V
{{\tt 434}} & 16,495  & 16,242  & {\color{blue}{75}} & {\color{blue}{7}} & {\color{blue}{5$\times$10$^{-3}$}} & {\color{blue}{5$\times$10$^{-4}$}}\\
{{\tt 435}} & 990,575 & 975,445  & {947} & {900} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
{{\tt 436}} & 1,160,742 & 1,143,078   & {3,914} & {3,843} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 437}} & 581,635 & 572,775 & {1,492} & {1,475}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 444}} & 591,201 & 582,229 & {294} & {281}  & {5$\times$10$^{-4}$} & {5$\times$10$^{-4}$}\\
{{\tt 445}} & 84,435  & 83,164  & {91} & {28}  & {1$\times$10$^{-3}$} & {3$\times$10$^{-4}$}\\
{{\tt 447}} & 521,846 & 513,493  & {150} & {108}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 450}} & 341,030 & 335,848  & {99} & {91}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 453}} & 258,797 & 254,496  & {623} & {582}  & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 454}} & 1,721,804 & 1,695,613  & {678} & {627}  & {4$\times$10$^{-4}$} & {4$\times$10$^{-4}$}\\
{{\tt 456}} & 410,533 & 404,328  & {85} & {50}  & {2$\times$10$^{-4}$} & {1$\times$10$^{-4}$}\\
{{\tt 458}} & 589,541 & 580,591  & {542} & {513} &  {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 459}} & 798,917 & 786,726  & {2,143} & {2,132}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 462}} & 595,188 & 586,120  & {3,326} & {3,274}  & {6$\times$10$^{-3}$} & {6$\times$10$^{-3}$}\\
{{\tt 464}} & 649,838 & 639,939  & {601} & {563}  & {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 465}} & 895,754 & 882,106  & {883} & {797}  & {1$\times$10$^{-3}$} & {1$\times$10$^{-3}$}\\
{{\tt 470}}	& 349,830 & 344,510 & {143} & {94} & {4$\times$10$^{-4}$} & {3$\times$10$^{-4}$}\\
{{\tt 471}} & 367,589 & 361,959  & {2,114} & {2,072} & {6$\times$10$^{-4}$} & {6$\times$10$^{-4}$}\\
{{\tt 473}} & 362,587 & 357,090  & {359} & {317} &  {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
%{{\tt 481}} & \multicolumn{4}{c}{Runtime Error}\\
{{\tt 482}} & 654,208	 & 644,223  & {2,436} & {2,392} &   {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\ %% V
%{{\tt 483}} & \multicolumn{4}{c}{Out-of-Scope}\\
{{\tt 998}} & 128	 & 127  & {0.6} & {0.6} &  {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 999}} & 128 &  127 & {0.8} & {0.6} &  {6$\times$10$^{-3}$} & {5$\times$10$^{-3}$}\\ \hline 
\multicolumn{3}{|r|}{Averages} & 852 & 815 &  {3$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ \hline
\end{tabular}
}
\caption{Performance Evaluation on the SPEC Benchmarks\label{tab:spec_real}}
\vspace{-0.25in}
\end{table}
